Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-08 Manuscript.Rmd
Thresholding fully checked. Small improvement to HCPOut

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307"){

  nVertices <- 59412
  tempVec <- rep(0, nVertices)
  temp <- grep(MOI, colnames(Data))
  tempVec[Data$Vertex] <- Data[[temp]]
  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")

>>>>

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){

  nVertices <- 59412
  tempVec <- rep(padding, nVertices)
  temp <- grep(MOI, colnames(Data))
  tempVec[Data$Vertex] <- Data[[temp]]
  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")
